---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# noga

<!-- badges: start -->
[![R-CMD-check](https://github.com/SwissStatsR/noga/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SwissStatsR/noga/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

The noga package allows recoding noga values to their labels or vice versa. [Noga](https://www.bfs.admin.ch/bfs/en/home/statistics/industry-services/nomenclatures/noga.html) is derived from the European classification system of economic activities (NACE). NOGA08 is the version currently supported in this package.

## Installation

You can install the noga package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("swissstatsr/noga")
```

The package is not yet available on CRAN.

## NOGA-levels

The Noga classification system has 5 levels which can be recoded with this package:

- section (a single alphabetic character from A to U)
- division (two digits 01-99)
- group (three digits 011-990)
- class (four digits 0111-9900)
- type (six digits 011100-990003)

Note that if you recode labels to values, the output variable will be in string format as the noga codes are essentially strings rather than a numeric.

## Usage

The function `noga::noga_recode()` recodes noga values to their labels or vice versa. Please note that the vector/variable you recode cannot contain multiple noga levels simultaneously. The function will not be able to recode a vector that contains both the noga-group and noga-class level. If all given labels are shared across several levels, the deepest (most specific) level will be used.

```{r example}
library(noga)

example.data <- data.frame(
  test1 = c(702, 62),
  test2 = c("Management consultancy activities", "Extraction of natural gas"),
  test3 = c("702", "062")
)

noga_recode(var=example.data$test1, language = "fr", level = "group", to = "auto")
noga_recode(var=example.data$test2, language = "en", level = "auto", to = "values")
noga_recode(var=example.data$test3, language = "de", level = "auto", to = "auto")
```

## Planned expansion for the future
- Aggregation function so that values/codes of one level can be aggregated to another one
- Include economic sectors (primary: raw material, secondary: manufacturing, tertiary: services)
- Include the Noga-50 level of the Swiss FSO that groups Switzerland's largest divisions so that they represent the 50 economic activities
- When available, include NOGA 2025 recoding (to/from labels and codes, to/from NOGA08)
