---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# noga

<!-- badges: start -->
[![R-CMD-check](https://github.com/SwissStatsR/noga/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SwissStatsR/noga/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

The noga package provides allows to recode noga values to its labels or vice versa. Noga is the European classification system of economic activies. The RMD check fails yet because the noga labels are not yet supplied in UTF-encoding because to guarantee readibility of the characters.

## Installation

You can install the development version of noga from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("swissstatsr/noga")
```

The package is not yet available on CRAN.

## NOGA-levels

The Noga clasisfication system has 5 levels which can be recoded with this package:
- section (alphabetic one character from A to U)
- division (two digits 01-99)
- group (three digits 011-990)
- class (four digits 0111-9900)
- type (six digits 011100-990003)

Note that if you recode labels to values, the output variable will be in string format as the noga-codes are essentially strings rather than a numeric.

## Usage

The function `noga::noga_recode` recodes noga values to their labels or vice versa. Please note that the vector/variable you recode cannot contain multiple noga-levels simultaneously. The function will not be able to recode a vector that contains both the noga-group and noga-class level.

```{r example}
library(noga)
 example.data <- data.frame(
test1 = c(702,62),
test2 = c("Management consultancy activities","Extraction of natural gas"),
test3=c("702","062"))
noga::noga_recode(var=example.data$test1,language="fr",level="group",to="auto")
noga::noga_recode(var=example.data$test2,language="en",level="auto",to="values")
noga::noga_recode(var=example.data$test3,language="de",level="auto",to="auto")
```

## Planned expansion for the future
- Aggregation function so that values/codes of one level can be aggregated to another one
- Include economic sectors (primary: raw material, secondary: manufacturing, tertiary: services)
- Include the Noga-50 level of the Swiss FSO that groups Switzerland's largest divisions so that they represent the 50 economic activities   
